### 2018-10-18 1/exams/m1.tex
Fix up solution to m1.

;; count : LoN -> Number
;; Count the number of non-negative numbers in list
(check-expect (count-non-neg '()) 0)
(check-expect (count-non-neg (list 1 -2 8 0)) 3)
(define (count-non-neg lon)
  (cond [(empty? lon) 0]
        [(cons? lon)
         (if (< (first lon) 0)
             (count-non-neg (rest lon))
             (add1 (count-non-neg (rest lon))))]))
\end{SaveVerbatim}

>>>>

;; sum-pos : LoN -> Number
;; Count the number of positive numbers in list
(check-expect (sum-pos '()) 0)
(check-expect (sum-pos (list 1 -2 8 0)) 9)
(define (sum-pos lon)
  (cond [(empty? lon) 0]
        [(cons? lon)
         (if (< (first lon) 0)
             (sum-pos (rest lon))
             (+ (first lon) (sum-pos (rest lon))))]))
\end{SaveVerbatim}
